---
title: Pre-tut setup
subtitle: West Lab, Dept. Biological Sciences, UCT
author: Ruan van Mazijk
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

Just some housekeeping to make sure the tut runs smoothly, you need the following installed and set up on your computer before we meet:

1. A recent version of R (ideally the latest version, available [here](https://cloud.r-project.org))
2. Ditto for [RStudio](https://www.rstudio.com/products/rstudio/download/). This is, in my opinion, the most user friendly and powerful environment in which to use R, and especially RMarkdown.
3. The R-package `rmarkdown`. This can be installed by running the following code in the console in a new R-session on your computer:

```{r}
install.packages("rmarkdown", dependencies = TRUE)
```

If you can open RStudio, run the following line in the console:

```{r}
"rmarkdown" %in% installed.packages()
```

and it returns `TRUE`, then you are good to go.
